The binary liquid model for gravity-driven microchannel simulations

### 2010-10-22 Text/paper.tex
Added capillary number script. Need to put some results in.

\section{Capillary number region}
The purpose of this section is to validate the correlations of
\citet{giavedoni-numerical}, Fig. \ref{fig:giavedoni:planar}, and
\citet{heil-bretherton}, Fig. \ref{fig:heil:planar}, for the range of capillary
numbers. Because of limiting computational factors ({\color{red} What is the
least capillary number which is OK?}) we cannot go to the range of small
capillary numbers. However, all the other methods were validated across the
small capilary numbers and extended for the range of capillary numbers from
$0.005$ to $1.0$. Our goal is to compare the film thickness over the capillary
range from $0.03$ to $1.0$.

To perform numerical simulations we refer to
grid refinement section where we obtained that the interface width should be
at most {\color{red} $40$} percent of the interface width. For the benchmark
results we
suggest the following Capillary numbers as:
\begin{equation}
0.03,0.05,0.08,0.1,0.2,0.4,0.6,0.8,1.0\, .
\end{equation}
The corresponding approximate film widths from \cite{giavedoni-numerical} are as
follows:
$0.04,0.06,0.08,0.1,0.12,0.13,0.15$. $5$ lattice boltzmann units occupy
{\color{red} Could be another number $40\%$} of the interface thickness.
Therefore the grid size should be as
following {\color{red} Michal, different numbers would be here.
$314\mathrm{x}4681$,$210\mathrm{x}3121$,
$158\mathrm{x}2341$, $127\mathrm{x}1876$, $106\mathrm{x}1561$,
$98\mathrm{x}1441$,$85\mathrm{x}1246$ Michal, for the larger capillary
numbers such small grid is not
appropriate because of the instabilities.
}.

{\color{red} Probably we don't need the explanations about initialization here,
just to present results}
To utilize previous results to properly initialize simulations to run one need
to do some modifications. The result is that for the grid with $H_{eff}=200$ we
obtained the film width as {\color{red} Will be another number $0.0685$} and
velocity in the center of the bubble as
{\color{red} Will be another number $0.0045$}. The force gradient was
{\color{red} Probably the same number $6\, 10^{-6} /16$}. The predicted
Capillary
number was $0.05$ and the actual one based on the center velocity calculation is
{\color{red} Will be another number $0.0795$}. However, we performed simulations
according the assumed value of $0.05$. Let us perform some correlations to
calculate how the system needs to be initialized. 
\begin{equation}
\begin{aligned}
&Ca_{lit} \propto U_{slug}\\
&U_{slug} \propto \frac{\mathrm{d}P}{\mathrm{d}x} N_y^2\\ 
&Ca_{lit} \propto \frac{\mathrm{d}P}{\mathrm{d} x} N_y^2 \text{ or }\\
&\frac{\mathrm{d}P}{\mathrm{d} x} \propto \frac{Ca_{lit}}{Ny^2},
\end{aligned}
\end{equation}
where the index $lit$ stands for the presented in the literature in
\cite{giavedoni-numerical,heil-bretherton}. Therefore the initialized consistent
pressure gradients can be taken from
previous consistent simulations:
\begin{equation}
\frac{\mathrm{d}P}{\mathrm{d} x}=6\,10^{-6}/16 \frac{Ca_{literature}}{0.05}
\frac{200^2}{N_y^2}=0.3 \frac{Ca_{literature}}{N_y^2}
\end{equation}
Note that $N_y$ is calculated through the expected resolution of the interface
in comparison with the interface thickness which itself is based on
Capillary number simulations. In terms of time the steady state successful
simulation for the grid $202\mathrm{x}3001$ was obtained after $200,000$ steps.
The physical
time is as follows:
\begin{equation}
\begin{aligned}
&\Delta t=\frac{U_{slug,LB} \Delta X}{U_{phys}} \propto \frac{1}{N_y-2}\\
&N_{iter}=200,000 \frac{N_y-2}{200}\approx 1000 N_y\\
%&N_{output}=51 Ny\\
\end{aligned}
\end{equation}

>>>>

\section{Capillary number region}
The purpose of this section is to validate the correlations of
\citet{giavedoni-numerical}, Fig. \ref{fig:giavedoni:planar}, and
\citet{heil-bretherton}, Fig. \ref{fig:heil:planar}, for the range of capillary
numbers. Because of limiting computational factors as memory and the
performance we cannot go to the range of small
capillary numbers. However, all the other methods were validated across the
small capilary numbers and extended for the range of capillary numbers from
$0.005$ to $1.0$. Our goal is to compare the film thickness over the capillary
range from $0.03$ to $1.0$.  For the
benchmark
results we
suggest the following Capillary numbers as:
\begin{equation}
0.03,0.05,0.08,0.1,0.2,0.4,0.6,0.8,1.0\, .
\end{equation}
The corresponding approximate film widths from \cite{giavedoni-numerical} are as
follows:
\begin{equation}
0.04,0.06,0.08,0.1,0.12,0.13,0.15\,.
\end{equation}
To perform numerical simulations we refer
to
grid refinement section where we obtained that the interface width should be
at most $50$ percent of the interface width. Therefore the grid was chosen as
$202 \mathrm{x} 3001$. $5$ lattice boltzmann units do not occupy more than $60$
percent of the effective width. Because the simulation get unstable with
smaller grids and larger gradients, all the capillary number simulations were
performed on the grid chosen. To properly initialize the force gradient the
proportionality law was utilized. For instance, with the forcing
$6\,10^{-6}/16$ was chosen for the grid to obtain predicted capillary number as
$0.005$. Therefore, one can obtain the initial forcing for other grids using
simple correlations: 
\begin{equation}
\begin{aligned}
&Ca_{lit} \propto U_{bubble}\\
&U_{bubble} \propto \frac{\mathrm{d}P}{\mathrm{d}x} N_y^2\\ 
&Ca_{lit} \propto \frac{\mathrm{d}P}{\mathrm{d} x} N_y^2 \text{ or }\\
&\frac{\mathrm{d}P}{\mathrm{d} x} \propto \frac{Ca_{lit}}{N_y^2},
\end{aligned}
\end{equation}
where the index $lit$ stands for the predicted capillary number
\cite{giavedoni-numerical,heil-bretherton}. The grid number $Ny$ is not
involved as because the simulations are conducted on the same grid.
Therefore,the pressure gradient can be obtained through the capillary numbers
ratio:
\begin{equation}
\frac{\mathrm{d}P}{\mathrm{d} x}=6\,10^{-6}/16 \frac{Ca_{lit}}{0.05}
\end{equation}
The film width is initialized through the capillary numbers ratio as well:
\begin{equation*}
w=12 \frac{Ca_{lit}}{0.05}
\end{equation*}
The results were obtained after $200,000$ steps.
The physical
time is as follows:
\begin{equation}
\begin{aligned}
&\Delta t=\frac{U_{slug,LB} \Delta X}{U_{phys}} \propto \frac{1}{N_y-2}\\
&N_{iter}=200,000 \frac{N_y-2}{200}\approx 1000 N_y\\
%&N_{output}=51 Ny\\
\end{aligned}
\end{equation}
